Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-16 arxiv/proof_gaussian_case.tex
appendix

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}

	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
			\begin{align}\label{lem_cov_derv_eq}
				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
			\end{align}
				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
			\begin{align}\label{eq_a34extra}
				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{align}

We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm,
$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
}$$

>>>>

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
We first state the bias limit for the term in equation \eqref{eq_bias_2task}.

\begin{theorem}\label{thm_main_RMT_app}
	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed unit vector $w\in\real^p$:
			\begin{align}\label{lem_cov_derv_eq}
				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
			\end{align}
				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
			\begin{align}\label{eq_a34extra}
				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{align}
\end{theorem}
In this section, we give the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}

\subsection{Proof Overview}
Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.

Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$. 
We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm,
$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
}$$
